\documentclass[11pt,letterpaper]{article}
\pdfoutput=1
\usepackage{jheppub}

\usepackage[utf8]{inputenc}

\usepackage{color}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{xspace}

\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[caption=false]{subfig}
\usepackage{url}
\usepackage{bbold}
\usepackage{slashed}
\usepackage{array}
\usepackage{hepunits}

\usepackage{multirow}
\usepackage{threeparttable}
\usepackage{paralist}

%\newcommand{\GeV}{\text{GeV}}
%\newcommand{\TeV}{\text{TeV}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\SM}{\text{SM}}

\newcommand{\U}{\text{U}}
\newcommand{\CKM}{\text{CKM}}
\newcommand{\eff}{\text{eff}}

\newcommand{\cO}{{\mathcal O}}

\newcommand{\genang}[2]{{\lambda^{#1}_{#2}}}

\newcommand{\lamqcd}{{\Lambda_\text{QCD}}}

\newcommand{\ev}{\text{event}}
\newcommand{\jet}{\text{jet}}
\newcommand{\jets}{\text{jets}}
\newcommand{\subj}{\text{subjet}}
\newcommand{\subjs}{\text{subjets}}
\newcommand{\cut}{\text{cut}}
\newcommand{\trim}{\text{trim}}
\newcommand{\Ecut}{E_{{\rm cut}}}

\newcommand{\ptc}{p_{T{\rm cut}}}
\newcommand{\ptsubc}{p_{T{\rm subcut}}}

\newcommand{\ecf}[2]{e_{#1}^{(#2)}} 
\newcommand{\ecfnobeta}[1]{e_{#1}} 

\newcommand{\sub}{\text{sub}}
\newcommand{\miss}{\text{miss}}

\newcommand{\pythia}{\textsc{Pythia~8}\xspace}
\newcommand{\herwig}{\textsc{Herwig~7}\xspace}
\newcommand{\eventtwo}{\textsc{Event2}\xspace}
\newcommand{\vincia}{\textsc{Vincia}\xspace}
\newcommand{\sherpa}{\textsc{Sherpa}\xspace}

\newcommand{\FastJet}{\textsc{FastJet}\xspace}
\newcommand{\MadGraph}{\textsc{MadGraph}\xspace}

\newcommand{\df}{\text{d}}
\newcommand{\vev}[1]{\langle #1 \rangle}


\DeclareRobustCommand{\Sec}[1]{Sec.~\ref{#1}}
\DeclareRobustCommand{\Secs}[2]{Secs.~\ref{#1} and \ref{#2}}
\DeclareRobustCommand{\Secss}[3]{Secs.~\ref{#1}, \ref{#2}, and \ref{#3}}
\DeclareRobustCommand{\App}[1]{App.~\ref{#1}}
\DeclareRobustCommand{\Tab}[1]{Table~\ref{#1}}
\DeclareRobustCommand{\Tabs}[2]{Tables~\ref{#1} and \ref{#2}}
\DeclareRobustCommand{\Fig}[1]{Fig.~\ref{#1}}
\DeclareRobustCommand{\Figs}[2]{Figs.~\ref{#1} and \ref{#2}}
\DeclareRobustCommand{\Figss}[3]{Figs.~\ref{#1}, \ref{#2}, and \ref{#3}}
\DeclareRobustCommand{\Eq}[1]{Eq.~(\ref{#1})}
\DeclareRobustCommand{\Eqs}[2]{Eqs.~(\ref{#1}) and (\ref{#2})}
\DeclareRobustCommand{\Eqss}[3]{Eqs.~(\ref{#1}), (\ref{#2}), and (\ref{#3})}
\DeclareRobustCommand{\Ref}[1]{Ref.~\cite{#1}}
\DeclareRobustCommand{\Refs}[1]{Refs.~\cite{#1}}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\nn}{\nonumber}

\renewcommand{\textfraction}{0.10}
\renewcommand{\topfraction}{0.90}
\renewcommand{\bottomfraction}{0.90}
\renewcommand{\floatpagefraction}{0.65}

%% Reference commands %%
\newcommand{\mb}[1]{\boldsymbol{#1}}
\newcommand{\bm}[1]{\boldsymbol{#1}}
\newcommand{\mbo}[1]{\boldsymbol{\overline{#1}}}

\usepackage{xspace}


\def\Tr{\mathop{\rm Tr}}
\newcommand{\rep}[1]{\mathbf{#1}}
\newcommand{\conjrep}[1]{\overline{\mathbf{#1}}}


\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\newcommand{\e}{\epsilon}
\newcommand{\D}{\Delta}
\renewcommand{\l}{\lambda}
\renewcommand{\th}{\theta}
\newcommand{\bq}{\bar{q}}
\newcommand{\zcut}{z_{\rm cut}}
\newcommand{\ycut}{y_{\rm cut}}

\newcommand{\IZ}{\mathbb{Z}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cF}{\mathcal{F}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cK}{\mathcal{K}}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}

\newcommand{\F}{\mathcal{F}}
\newcommand{\Ft}{\widetilde{\mathcal{F}}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\Gt}{\widetilde{\mathcal{G}}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\HHt}{\widetilde{\mathcal{H}}}
\newcommand{\ord}[1]{\mathcal{O}\!\left(#1\right)}

\newcommand*\numcircledmod[1]{#1 \!\!\! \bigcirc}

\newcommand{\Njet}{\widetilde{N}_{\rm jet}}
\newcommand{\dN}[1]{\Delta_{#1}}
\newcommand{\dNpm}{\Delta_{2\pm}}
\newcommand{\dNp}{\Delta_{2+}}
\newcommand{\dNm}{\Delta_{2-}}
\newcommand{\dNtm}{\Delta_{3-}}

\newcommand{\cT}{\mathcal{T}}
%\newcommand{\as}{\alpha_s}
\renewcommand{\angle}{\theta}

%\definecolor{darkgreen}{rgb}{0,0.5,0}
%\newcommand{\jdt}[1]{\textbf{\textcolor{darkgreen}{(#1 --jdt)}}}
%\newcommand{\gs}[1]{\textbf{\textcolor{darkblue}{(#1 --gs)}}}

\definecolor{mildred}{rgb}{0.8,0,0}
\newcommand{\info}[1]{\textbf{\textcolor{mildred}{(#1)}}}

\definecolor{llblue}{rgb}{0,0.5,1.0}
\newcommand{\ijm}[1]{\textbf{\textcolor{llblue}{(#1 --ijm)}}}

\definecolor{darkgreen}{rgb}{0,0.6,0.0}
\newcommand{\gs}[1]{\textbf{\textcolor{darkgreen}{(#1 --gs)}}}

\begin{document}


\title{Towards Extracting the Strong Coupling Constant \\ from Jet Substructure at the LHC}

%\author[a]{Grigorios Chachamis,}
\author[a]{Suman Chatterjee,}
\author[d]{Fr\'{e}d\'{e}ric Dreyer,}
\author[e]{Maria Vittoria Garzelli,}
\author[d]{Philippe Gras,}
\author[e]{Andrew Larkoski,}
%\author[g]{Daniel Maitre,}
\author[g]{Simone Marzani,}
\author[h]{Ian Moult,}
\emailAdd{ianmoult@lbl.gov}
\author[h]{Ben Nachman,}
\emailAdd{bpnachman@lbl.gov}
\author[i]{Andrzej Si\'{o}dmok,}
\author[j]{Andreas Papaefstathiou,}
\author[j,f]{Peter Richardson,}
\author[a]{Tousik Samui,}
\author[k]{Gregory Soyez,}
\emailAdd{gregory.soyez@ipht.fr}
\author[b]{and Jesse Thaler}
\emailAdd{jthaler@mit.edu}

%\affiliation[a]{Instituto de F\'{i}sica Te\'{o}rica UAM/CSIC \& Universidad Aut\'{o}noma de Madrid, Madrid, Spain}
\affiliation[a]{Tata Inst. of Fundamental Research, Mumbai, India}
\affiliation[b]{Center for Theoretical Physics, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
\affiliation[c]{II. Institute for Theoretical Physics, Hamburg University Luruper Chaussee 149, D-22761 Hamburg, Germany}
\affiliation[d]{IRFU, CEA, Universit\'{e} Paris-Saclay, Gif-sur-Yvette, France}
\affiliation[e]{Physics Department, Reed College, Portland, OR 97202, USA}
\affiliation[f]{IPPP, Department of Physics, Durham University}
\affiliation[g]{Dipartimento di Fisica, Universit\'{a} di Genova and INFN, Sezione di Genova, Via Dodecaneso 33, 16146, Italy}
\affiliation[h]{Physics Division, Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley, CA, 94720, USA}
\affiliation[i]{The Henryk Niewodniczanski Institute of Nuclear Physics in Cracow, Polish Academy of Sciences}
\affiliation[j]{Theoretical Physics Department, CERN, CH-1211 Geneva 23, Switzerland}
\affiliation[k]{IPhT, CEA Saclay, CNRS UMR 3681, F-91191 Gif-sur-Yvette, France}

\abstract{
Recent advances in jet substructure have introduced a new class of jet observables that are amenable to systematically improveable calculations in the complex environment of the Large Hadron Collider (LHC). These observables exploit grooming to reduce non-perturbative contributions, and simplify perturbative calculations. With these recent advances in both theory and experiment, we believe that it is the appropriate time to start to investigate the possibility of extracting the strong coupling constant $\alpha_s$ from jet substructure.  In this paper we perform a proof-of-principle sensitivity study to demonstrate the suitability of such measurements to add useful information to the existing precision extractions of $\alpha_s$. We highlight a number of theoretical and experimental advantages of groomed observables for $\alpha_s$ extractions, and discuss several difficulties of the LHC environment.   Using a simplified approach, we show that a measurement of $\alpha_s$ with an approximate 10\% uncertainty should be possible at the LHC.  This result motivates a complete analysis with a full set of experimental and theoretical considerations, and we present a number of directions where improvements on both the theory and experiment sides could be made in the near future.
}

\maketitle

\section{TODO}

\begin{itemize}
\item Cut off Fig.~\ref{fig:sensitivity} and Fig.~\ref{fig:robustness} at -12.  Also, add a statement or plot about Pythia.
\end{itemize}

\clearpage

%%==============
\section{Introduction}
%%==============

\input{sections/introduction.tex}

%%==============
\section{Observable and Algorithm Definitions}
\label{sec:definitions}
%%==============

\input{sections/obs_definition.tex}

%%==============
\section{Grooming Away Soft Complications}
\label{sec:softcomplications}
%%==============

\input{sections/softcomplications.tex}

%%==============
\section{Observable Sensitivity to $\alpha_s$}
\label{sec:jetmass}
%%==============

\input{sections/casestudy.tex}

\clearpage

%%==============
\section{Idealized Performance at the LHC}
\label{sec:ben_study}
%%==============

\input{sections/lhc.tex}

%%==============
%\section{Assessing Theoretical Uncertainties}
%%==============

%\input{sections/theoryuncerts}

%%==============
%\section{Alternative Observables}
%%==============

%\input{sections/alternatives}

%%==============
%\section{Estimated Sensitivity from Parton Showers}
%%==============

%\input{sections/partonshowerstudy.tex}

%%==============
%\section{Prospects at Lepton Colliders}
%%==============

%\input{sections/epluseminus.tex}

\clearpage

%%==============
\section{Conclusions and Future Outlook}
%%==============
\label{sec:future}
%\info{All}

In this paper we have performed a preliminary study of the possibility of performing an extraction of the strong coupling constant $\alpha_s$ from groomed jet substructure measurements at the LHC.  This has been made possible by recent advances in the calculation of groomed event shapes, which allow them to be resummed to NNLL accuracy, as well as advances in the understanding of the experimental uncertainties for groomed jet observables. 

We have highlighted a number of features that an extraction of
$\alpha_s$ from groomed substructure would offer. In particular, the
grooming procedure suppresses non-perturbative hadronization
corrections to the mass distribution extending the range of
perturbative control by up to a factor of $\sim 100$ as compared to the ungroomed case, where hadronization corrections are a dominant uncertainty. Furthermore, the nature of the non-perturbative corrections is completely different, and therefore a groomed extraction could provide complementary information. 

Using the groomed jet mass as a concrete example, we have performed a feasibility study for the extraction of $\alpha_s$ from groomed jet substructure. Taken separately, the groomed quark and gluon distributions both exhibit good sensitivity to $\alpha_s$. However, this study also highlighted a key issue relevant at the LHC. The leading behavior of the shape of the distribution is sensitive to the product $\alpha_s C_i$, where $C_i$ is the color Casimir, namely $C_A$ for gluon jets and $C_F$ for quark jets. This immediately implies that there is a degeneracy between the value of $\alpha_s$ and the quark gluon fraction of the sample. We highlighted two ways of overcoming this, either a fixed order calculation of the quark and gluon fractions, or the measurement of different observables, which enables a breaking of this degeneracy. This would ideally be combined with multiple samples with (relatively pure~\cite{Gallicchio:2011xc}) quark/gluon fractions.  Significantly better precision is achieved by the explicit calculation, however, this also introduces a stronger dependence on the PDFs which should then ideally be simultaneously fitted.

With currently achievable experimental and theoretical uncertainties, we have shown that an extraction of $\alpha_s$ at the $10\%$ level is feasible using the currently available data at the LHC.  We believe that this study motivates a serious effort to extract the strong coupling constant, $\alpha_s$ from jet substructure at the LHC using groomed jet shapes. A serious analysis will require advances on both the theory and experiment side. We therefore conclude by discussing some of the major obstacles that must be overcome.

%\ijm{Ben will say something about experiment}


On the theory side, we can separately discuss the three primary aspects of the calculation:

\vspace{5mm}

\noindent {\bf Resummation Accuracy:} For $e^+e^-$ event shapes, the current state of the art is N$^3$LL. This has been achieved only for a few select observables using the soft collinear effective theory. The extension  to N$^3$LL accuracy for the groomed jet mass would require only the calculation of the anomalous dimensions for the groomed soft function to three-loop. This could be performed using currently available techniques, and would enable N$^3$LL accuracy. 

At this level of accuracy it will also be important to asses perturbative power corrections in $\zcut$.  Reference~\cite{Marzani:2017kqd,Marzani:2017mva} has shown that these corrections are numerically small.  However, if multiple $z_\text{cut}$ values are used that are not much less than one, these may be important.

\vspace{5mm}

\noindent {\bf Fixed Order Matching:} A key aspect, and potential complication to achieve a competitive theoretical accuracy as for $e^+e^-$ is the fixed order matching. For $e^+e^-$  the perturbative corrections to $e^+e^- \to$ 3 jets are known to NNLO \cite{GehrmannDeRidder:2007hr,Gehrmann-DeRidder:2007nzq,Weinzierl:2008iv,Weinzierl:2009ms}. To achieve a similar perturbative accuracy for the matching for the groomed jet mass will require $2\to 3$ matrix elements at NNLO. While results for the amplitudes are just becoming available \cite{Gehrmann:2015bfy,Dunbar:2016aux,Badger:2013yda,Badger:2017jhb,Abreu:2017hqn}, it will be a while before numerically efficient evaluations of the relevant cross sections are available. We believe that this is currently the theoretically most difficult ingredient. 

\vspace{5mm}

\noindent {\bf Non-Perturbative Corrections:} Finally, in addition to improving our understanding of the perturbative accuracy of the observable, it will also be crucial to improve our understanding of the non-perturbative aspects of groomed observables. While it has been shown through Monte Carlo studies that non-perturbative effects are suppressed throughout a large component of the distribution, it will be important to quantify this further. In the case of $e^+e^-$ event shapes, operator definitions of soft matrix elements allow for field theoretic definitions of the non-perturbative parameters. Ideally this could also be performed for groomed observables, placing the groomed jet mass on a firmer theoretical footing.

\vspace{5mm}

Experimentally, there are three broad topics that need to be addressed for a precision extraction of $\alpha_s$:

\vspace{5mm}

\noindent {\bf Mass Scale Uncertainties:} At the moment, ATLAS~\cite{Aaboud:2017qwh} and CMS~\cite{CMS-PAS-SMP-16-010} have very different approaches for determining the jet mass scale uncertainty, both with known limitations.  CMS performs a fit to the hadronic $W$ boson mass peak in one-lepton $t\bar{t}$ events and takes the shift in the peak position as the uncertainty in the jet mass scale (which is negligible and thus ignored)~\cite{Sirunyan:2016cao}.  Two challenges with this approach are that (a) the peak position is a convolution of particle-level and detector-level effects and (b) it is not clear that uncertainties derived for boosted $W$ bosons should be the same as for generic quark and gluon jets at all masses.  One can overcome (a) with a technique like forward-folding~\cite{ATLAS-CONF-2016-008,ATLAS-CONF-2016-035}.  Various PS MC generators are studied, but it is likely not sufficient to have one global model comparison.  The impact on the jet mass resolution in one topology may be completely different than the impact of the scale, resolution, or acceptance in another topology.  In contrast, the ATLAS measurement propagates constituent-based uncertainties through to the groomed mass.  These uncertainties are derived from matching tracks to calorimeter-cell clusters and studying the energy and angular matching.  Studies have shown that this `bottom-up' approach works well for reproducing the jet energy scale~\cite{Aaboud:2016hwh}, which has been validated also for groomed jets in Ref.~\cite{Aaboud:2017qwh}.  However, this does not hold exactly for the mass, which is not linear in the constituent energies~\cite{Nachman:2016qyc}.   The uncertainties are validated using the standard ATLAS approach using track-jets~\cite{Aad:2013gja,ATLAS-CONF-2017-063}, but to achieve higher precision, a more detailed understanding of the impact of energy thresholds, fluctuation correlations and calorimeter cluster merging will be required.

\vspace{5mm}

\noindent {\bf Mass Resolution Uncertainties:} ATLAS and CMS use the same approaches for the resolution as for the scale (bottom-up and $W$ mass peak).  ATLAS validates their approach in a similar manner as CMS, by using the $W$ mass peak from $t\bar{t}$ events.\footnote{This validation does not have the same complete forward-folding machinery as was used by ATLAS for trimmed jets.}  The mass resolution is mostly not the limiting factor, but it could be if the situation is not improved as the jet mass scale precision improves. 

\vspace{5mm}

\noindent {\bf Pileup Modeling and Mitigation:} Grooming significantly reduces the impact of pileup, but if the Run 3+ data are to be used (pileup levels of 80+), then a significantly better and more detailed understanding of the degradation due to pileup will be required.  Statistical are currently not dominant, so it is conceivable that the higher instantaneous luminosity data is not used for the precision $\alpha_s$ extraction.  This may change if one wants to exploit the largest lever-arm possible; to access the highest $p_\text{T}$ jets, we will need more data.

\vspace{5mm}

It would also be interesting to study in more detail the use of other groomed observables. Since it may be the case that it is ultimately experimental uncertainties that are the limiting factor, one potentially interesting direction is the use of track based measurements. From the experimental perspective, this significantly reduces uncertainties, particularly in a high pile up environment. From the theoretical side, it introduces the need for non-perturbative track functions. However, for specific observables, only certain moments of the track functions are required. This therefore offers the potential that combined fits for the moments of the track functions and $\alpha_s$ could be performed, much like how fits are performed for $e^+e^-$ event shapes. Significantly more theoretical work is required to see if this is truly a viable possibility, although we believe that this is well motivated.


We are optimistic that these difficulties on both the theory and experiment side can be overcome, enabling a precision probe of the strong coupling constant from jet substructure in the LHC environment.

\begin{acknowledgments}

The work of GS is supported in part by the French Agence Nationale de la Recherche,
under grant ANR-15-CE31-0016, and by the ERC Advanced Grant Higgs@LHC
(No.\ 321133).
%
The work of JT is supported by the DOE under grant contract numbers DE-SC-00012567 and DE-SC-00015476.
%
IM and BN are supported in part by the Office of High Energy Physics of the U.S. Department of Energy under Contract No. DE-AC02-05CH11231, and the LDRD Program of LBNL.

\end{acknowledgments}

\bibliographystyle{jhep}
\bibliography{lh2017_alphas}

\end{document}
