
In this section, we briefly review the definitions of the observables and grooming procedures that we will focus on in this paper.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Observables}\label{sec:shape_def}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A simple class of jet shape observables that have sensitivity to the value of $\alpha_s$ are two-point correlation functions~\cite{Banfi:2004yd,Larkoski:2013eya}.
%
There has been significant theoretical study of these objects, and their perturbative behavior is understood to relatively high accuracy.
%
For a set of constituents $\{i\}$ in a jet $J$, the two-point correlation functions in $pp$ collisions are defined as
%
\begin{align}
\label{eq:ppe2}
\left.\ecf{2}{\alpha}\right|_{pp}&=\frac{1}{p_{TJ}^2}\sum_{i<j\in J} p_{Ti} \, p_{Tj} \, \left(\frac{R_{ij}}{R}\right)^\alpha\,, 
\end{align}
where $p_{Ti}$ is the transverse momentum of particle $i$ with respect to the beam axis, $p_{TJ}$ is the transverse momentum of the jet, $R_{ij}$ is the distance between particles $i$ and $j$ in the rapidity-azimuthal angle plane, and $R$ is the jet radius.
%
Note that some authors define the correlation functions without the $R^\alpha$ factor in the denominator.
%
The angular exponent $\alpha$ is a parameter that controls sensitivity to wide-angle emissions.
%
If all emissions in the jet are nearly collinear, then the two-point energy correlation function reduces to a function of the jet mass ($m$) when $\alpha=2$:
\begin{equation}
\ecf{2}{2} \sim \frac{m^2}{R^2\, p_{T}^2}\,.
\end{equation} 

In this paper, we primarily restrict ourselves to the case of $\alpha=2$ as this has been the focus so far from both the theoretical~\cite{Frye:2016okc,Frye:2016aiz,Marzani:2017kqd,Marzani:2017mva} and experimental~\cite{Aaboud:2017qwh,CMS-PAS-SMP-16-010} communities.
%
However, it is interesting to study if other values of $\alpha$ could provide improved sensitivity to $\alpha_s$.
%
Another benchmark value is $\alpha=1$, which corresponds to $k_T$ (or broadening) instead of mass.
%
The two-point correlation functions are closely related to the jet angularities~\cite{Berger:2003iw,Almeida:2008yp,Ellis:2010rwa,Larkoski:2014pca}, with the latter being defined with respect to a jet axis.

%a broadening or $k_T$ type measure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Grooming Techniques}\label{sec:groom_tech}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

There are a variety of jet grooming techniques to mitigate soft and wide-angle jet contamination~\cite{Butterworth:2008iy,Ellis:2009su,Ellis:2009me,Krohn:2009th,Dasgupta:2013ihk,Larkoski:2014wba}.
%
We focus here on the Soft Drop algorithm~\cite{Larkoski:2014wba}, defined using Cambridge/Aachen (C/A) reclustering \cite{Dokshitzer:1997in,Wobisch:1998wt,Wobisch:2000dk}.
%
Starting from a jet identified with an IRC-safe jet algorithm (such as anti-$k_t$ \cite{Cacciari:2008gp}), Soft Drop proceeds as follow:
%
\begin{enumerate}
%
\item Recluster the jet using the C/A clustering algorithm, producing an angular-ordered branching history for the jet.
%
\item Step through the branching history of the reclustered jet.  At each step, check the Soft Drop condition
%
\begin{align}\label{eq:sd_cut}
\frac{\min\left[ p_{Ti}, p_{Tj}  \right]}{p_{Ti}+p_{Tj}}> \zcut \left(   \frac{R_{ij}}{R}\right)^\beta \,,
\end{align}
%
where $\zcut$ is a parameter defining the scale below which soft radiation is removed, and $\beta$ is an exponent that controls the angular scale for removal.
%
If the Soft Drop condition is not satisfied, then the softer of the two branches is removed from the jet.  This process is then iterated on the harder branch.
%
\item The Soft Drop procedure terminates once the Soft Drop condition is satisfied.
%
\end{enumerate}
%
This procedure generalizes the modified Mass Drop Tagger (mMDT)~\cite{Dasgupta:2013ihk}, which corresponds to $\beta=0$ in the Soft Drop procedure described above.
%
Note that non-global logarithms~\cite{Dasgupta:2001sh} are formally removed from the soft drop mass distribution, even when $\beta>0$ (though clearly they are resorted as $\beta\rightarrow\infty$).

%Specializingto the case of $\beta=0$, where Soft Drop is equivalent to Modified Mass Drop Tagger~\cite{Dasgupta:2013ihk}, the algorithm proceeds as follows: \gs{The descriptino below is valid for any $\beta$, so I'd just drop the $\beta=0$ part here and mention, below the description ``This generalises the modified Mass Drop Tagger~\cite{Dasgupta:2013ihk} which corresonds to $\beta=0$ in the Soft Drop procedure described above.''}

%For $\beta=0$ non-global logarithms are removed from the distribution.  \gs{This is a bit misleading: NGLs are also formally removed from Soft  Drop with $\beta>0$}




